Supervised Learning for Psychological Attention to High School Students

### 2020-11-18 article/article.tex
[ article ] Added abstract and keywords.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
  Hello.
\end{abstract}

\begin{IEEEkeywords}
  Nice.
\end{IEEEkeywords}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
  In this article, three different machines are used to do supervised learning
  in a dataset recollecting important variables surrounding mental health and
  diagnostic prediction. Outputs such as ROC curves, output contours and
  classifier performance was realized to measure the performance of each
  machine. Lastly, it was concluded that the Decision Tree was the learning
  machine that performed the best and that the variable Emotional Socialization
  is the most important variable to classify the data points.
\end{abstract}

\begin{IEEEkeywords}
  Supervised learning, mental health, binary classification, high dimensional
  data, embedded data, psychological attention
\end{IEEEkeywords}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
